How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-05 tse-paper/content.tex
speaking variable names & consistent cursiveness

\begin{figure*}[tb]
\begin{algorithmic}[1]
\ForEach{technique $\in\{PBE,CTS,KWS,RLR\}$}
 \ForEach{project  $\in$ \emph{LogChunks}}
 \Comment{$|\emph{LogChunks}|$=80}
  \For{$i\gets 1, 5$}
   \State $logs \gets getBuildLogsByTime(project, i)$  \Comment{Logs
   returned ordered by time of creation.}
   \State $rlog \gets  getBuildLogsByTime(project, 6)$
   \State $n \gets |structuralCategories(logs)|$
   \State
   \State $train(technique, logs)$
       \State $retrievedLines \gets run(technique, rlog)$
       \State $metrics \gets calculateMetrics(retrievedLines,
       desiredLines(rlog))$
       \State
       \State $saveMetrics(technique, project, n, i, metrics)$

@@

In the following, we explain our study design
and introduce the metrics that
we measure to answer RQ2.
\Cref{fig:study} depicts the individual steps of our study as an
algorithmic procedure.

For each chunk retrieval technique and each project, we create
training example sets consisting of 1, 2, \dots 5 examples (lines
\circlenum{1}--\circlenum{3}).
We vary the training set size to measure how many examples we need to
confidently configure a technique, adressing \textbf{RQ2.1}.

@@

In the next step, we configure the chosen chunk retrieval technique with
the examples from the training set \circlenum{8} and run the technique
on the
training set, producing the retrieval output \circlenum{9}.

>>>>

\begin{figure*}[tb]
\begin{algorithmic}[1]
\ForEach{$technique \in\{PBE,CTS,KWS,RLR\}$}
 \ForEach{$project  \in \emph{LogChunks}$}
 \Comment{$|\emph{LogChunks}|$=80}
  \For{$i \in\{1,2,3,4,5\}$}
   \State $training\_logs \gets getBuildLogsByTime(project, 0, i)$
   \Comment{Logs
   returned ordered by time of creation.}
   \State $test\_log \gets  getBuildLogByTime(project, i)$
   \State $n \gets |structuralCategories(test\_logs)|$
   \State
   \State $train(technique, training\_logs)$
       \State $retrievedLines \gets run(technique, test\_log)$
       \State $metrics \gets calculateMetrics(retrievedLines,
       desiredLines(test\_log))$
       \State
       \State $saveMetrics(technique, project, n, i, metrics)$

@@

In the following, we explain our study procedure
and introduce the metrics that
we measure to answer RQ2.
\Cref{fig:study} depicts the individual steps of our study as an
algorithmic procedure.

For each chunk retrieval technique and each project, we create
training example sets consisting of 1, 2, \dots 5 examples (lines
\circlenum{1}--\circlenum{3}).
We vary the training set size to measure how many examples we need to
confidently configure a technique, addressing \textbf{RQ2.1}.

@@

In the next step, we configure the chosen chunk retrieval technique with
the examples from the training set \circlenum{8} and run the technique
on the
test set, producing the retrieval output \circlenum{9}.
